MLB Team Statistics between 2000 - 2023 on Predicting Games Won per Season ^[Code and data are available at: https://github.com/YcartXin/MLB_Team_Stats]

### 2024-04-13 paper/paper.qmd
Finished downloading, cleaning, and testing data. Data section in progress.

---
title: "MLB Team Statistics between 2000 - 2023 on Predicting Games Won per Season ^[Code and data are available at: https://github.com/YcartXin/MLB_Team_Stats]"
author: 
  - Tracy Yang
date: today
date-format: long
abstract: "Using MLB key team statistics between 2000 and 2023, this paper investigates the outcome of the 2024 season using each team's current statistics on predicting their total wins out of 162 games. We also investigate the common conception that baseball is a numbers game by evaluating the predictability of wins that a team would obtain during a seasion from looking at their batting average (AVG), defensive efficiency ratio (DffEff), and earned run average (ERA)."
format: 
  typst:
    toc: true
number-sections: true
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false

@@

Important statistics for a team in this paper is defined as the team's batting average (AVG), defensive efficiency ratio (DffEff), and earned run average (ERA). These three statistics each refer to an important aspect of a strong team: hitting, pitching, and fielding prospectively, hence important indicators on the wins a team is predicted to earn in a season. The specifics of these indicators will be elaborated on in @sec-data. Among present research, 2024 season predictions exist, however, they mainly focus on the win for a game or series for betting purposes. This paper is unique in its approach to predict and investigates the predictability of overall seasonal wins for baseball teams.

@@

Talk more about it.

And also planes. (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

>>>>

---
title: "MLB Team Statistics between 2000 - 2023 on Predicting Games Won per Season ^[Code and data are available at: https://github.com/YcartXin/MLB_Team_Stats]"
author: 
  - Tracy Yang
date: today
date-format: long
abstract: "Using MLB key team statistics between 2000 and 2023, this paper investigates the outcome of the 2024 season using each team's current statistics on predicting their total wins out of 162 games. We also investigate the common conception that baseball is a numbers game by evaluating the predictability of wins that a team would obtain during a seasion from looking at their batting average (AVG), defensive efficiency ratio (DefEff), and earned run average (ERA)."
format: 
  typst:
    toc: true
number-sections: true
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false

@@

Important statistics for a team in this paper is defined as the team's batting average (AVG), defensive efficiency ratio (DefEff), and earned run average (ERA). These three statistics each refer to an important aspect of a strong team: hitting, pitching, and fielding prospectively. A baseball team cannot succeed with a weak end in any of the three categories. Therefore, these are important indicators on the estimand - the wins a team would achieve by the end of the 2024 seasons among 162 games. The specifics of these indicators will be elaborated on in @sec-data. Among present research, 2024 season predictions exist, however, they mainly focus on the win for a specific game or series for betting purposes, focusing on the player data. This paper is unique in its approach to predict and investigates the predictability of overall seasonal wins for baseball teams.

@@

The data used in this analysis of different statistics on MLB Teams are sourced from Sports Reference, more specifically, Baseball Reference (). The data available on Baseball Reference is gathered by many contributors through a variety of sources such as the Lahmen database, and much of older data is accessed from third-party websites such as Retrosheet (). Baseball Reference stores and manipulate the data gathered using MySQL (). The data sets used in this investigation focus on the team statistics of the 30 teams in MLB and span from 2000 to 2010. The data sets were downloaded separately for each year among the batting, pitching, and fielding data. They were then combined into the final data set during the cleaning process. This analysis will be carried out in **R** @R using packages **tidyverse** @tidyverse, **dplyr** , **ggplot2** @ggplot2, **knitr** , **here **  XX.
